Wissenschaftliches Arbeiten

### 2014-06-29 paper.tex
Fixing an argument

At combinatorial auctions this task becomes much more cumbersome because each combination of bids $S \subseteq G$ must be tested against. \cite[pp.~46--47]{BCE12} shows that this ``Winner Determination Problem'' can be converted into the ``Set Packing Problem'' which is known to be NP-hard.

>>>>

At combinatorial auctions this task becomes much more cumbersome because each combination of bids $S \subseteq G$ must be tested against. \cite[pp.~46--47]{BCE12} shows that the known ``Set Packing Problem'' can be converted to this ``Winner Determination Problem''. The ``Set Packing Problem'' is known to be NP-complete and so the ``Winner Determination Problem'' is also NP-complete.
